Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia

### 2017-06-28 doc/manuscript/manuscript.Rmd
Add seeds to MLG-distribution
add fig 7 to manuscript

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed severity, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.032 (P = 0.001).
The marginal effects of state, host, and year were also significant (P = 0.001), but virulence was not significant (P = 0.045).
Much of the variation appears to be driven by isolates from Mexico (Fig. 7) and 2005, but it's worth noting that all Mexican isolates were collected in 2005.
Variance partitioning of the independent variables indicated virulence to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.

>>>>

The dbRDA was performed on clone-corrected isolates (N = 318) after grouping them by location, host, region, and year.
The forward-backward selection process revealed severity, year, region, and host to be the optimal variables for the reduced model, accounting for 17.6% of the variation.
ANOVA revealed that the reduced model was significant with an adjusted R^2^ of 0.032 (P = 0.001).
The marginal effects of state, host, and year were also significant (P = 0.001), but virulence was not significant (P = 0.045).
Much of the variation appears to be driven by isolates from Mexico (Fig. \@ref(rda-biplot)) and 2005, but it's worth noting that all Mexican isolates were collected in 2005.
Variance partitioning of the independent variables indicated virulence to be the least influential factor with 0.1% contributing to explaining the variation of molecular data whereas the combination of variables accounted for 3.3%.

![
Biplot showing 10 most influential explanatory variables (arrows) overlayed on the first two eigenvectors of distance based redundancy analysis of *S. sclerotiorum* isolates. 
The length of the arrows are directly proportional to the strength of the correlation between explanatory and molecular variables. 
Points represent the 318 clone-corrected samples in ordination space. 
](../../results/figures/publication/Figure7Z.pdf){#rda-biplot width=50%}
